Visual proteomics using whole-lamella 2D template matching

### 2022-01-03 manuscript.tex
Initial code [ci skip]
This build is based on
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/62df8f94079cea91a7ff27395620b6520811c5b5.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/62df8f94079cea91a7ff27395620b6520811c5b5/checks
https://github.com/jojoelfe/fowl_template_matching_manuscript/actions/runs/1650789776

This manuscript
(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/d1e11cd25750e43c45aa7a3781790ef34ec0a49f/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/d1e11cd25750e43c45aa7a3781790ef34ec0a49f}{jojoelfe/fowl\_template\_matching\_manuscript@d1e11cd}
on January 3, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/62df8f94079cea91a7ff27395620b6520811c5b5/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/62df8f94079cea91a7ff27395620b6520811c5b5}{jojoelfe/fowl\_template\_matching\_manuscript@62df8f9}
on January 3, 2022.
